### 2013-06-20 trunk/network-science/paper.tex

\newcommand\Mark[1]{\textsuperscript#1}
\numberwithin{equation}{section}
\mathtoolsset{centercolon}
\bibliographystyle{plain}

@@

\begin{center} %<<< Title
	\Large \textbf{\textsf{
		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
	\small
		Pufan He\Mark{1}, Yichao Zhou\Mark{2}, Qiwei Feng\Mark{3},
		Yu Yan\Mark{4}, Qingyang Li\Mark{5} and Xin Xing\Mark{6}\\[1em]
	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
		\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
		\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
		\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline

		\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
		\href{mailto:591527324@qq.com}{591527324@qq.com} &
		\href{mailto:823291634@qq.com}{823291634@qq.com}
	\end{tabular} \\[1em]

	\normalsize IIIS, Tsinghua University \\[1em]
\end{center} \par %>>>

>>>>

\newcommand\upper[1]{\textsuperscript#1}
\numberwithin{equation}{section}
\mathtoolsset{centercolon}
\bibliographystyle{plain}

@@

\begin{center} %<<< Title
	\Large \textbf{\textsf{
		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
	\small
		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
		\upper{1}\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
		\upper{2}\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline

		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
		\upper{5}\href{mailto:591527324@qq.com}{591527324@qq.com} &
		\upper{6}\upper{1}\href{mailto:823291634@qq.com}{823291634@qq.com}
	\end{tabular} \\[1em]

	\normalsize IIIS, Tsinghua University \\[1.5em]
\end{center} \par %>>>
